### 2021-02-08 manuscript.tex
language progress

Redundancy reduction was acheived within scipt functionality and storage utilization. Dedicated script actions that performed house keeping functions, as seen in the~\texttt{build\_table.sh} and~\texttt{backup.sh} (see Figure~\ref{fig:subroutine}), made specific effort to clear all transient data content that otherwise did not require persistent storage. This accounted for a large portion of persistent data that was previously left on the server. Additionally, script reduction was improved through a reorganzition of the general subroutines within the application. A reassignment of script actions were assigned in a more cohesive manner which allowed for both improved simplicity and modularity. This is most effectively seen in the manual control~\texttt{ccge\_upload.sh} script as the developer has the flexibility to opt out of executing several functions within the app.

@@

>>>>

Redundancy reduction was acheived within scipt functionality and storage utilization. Dedicated script actions that performed house keeping functions, as seen in the~\texttt{build\_table.sh} and~\texttt{backup.sh} (see Figure~\ref{fig:subroutine}), made specific effort to clear all transient data content that otherwise did not require persistent storage. This accounted for a large portion of persistent data that was previously left on the server. Additionally, script reduction was improved through a reorganzition of the general subroutines within the application. A reassignment of script actions were assigned in a more cohesive manner which allowed for both improved simplicity and modularity. This is most effectively seen in the manual control~\texttt{ccge\_upload.sh} script as the developer has the flexibility to opt out of executing several functions within the app (see Figure~\ref{fig:subroutine}).

@@

Improvements to the core achritecture stand as the central accomplishments in undertaking this project.
